Ages of Young Stars and Planets in the Kepler Field

### 2024-06-07 paper/ms.tex
update ms

\author[0000-0002-0514-5538]{Luke~G.~Bouma}
\altaffiliation{51 Pegasi b Fellow}
\affiliation{\caltech}
%\affiliation{51 Pegasi b Fellow}

%\author{and coauthors, including but not limited to...}

@@

%\author{and to be confirmed:}
%\affiliation{\caltech}

@@

%  \author[0000-0003-1298-9699]{Kento Masuda} ?
%  \affiliation{\osaka}

@@

{\it Field star ages from other surveys}:
While this study focused on Kepler, other photometric surveys
(e.g.~K2, TESS, HAT, WASP, NGTS, ZTF, ATLAS) open opportunities for
age-dating a far broader set of stars and planets.  Future prospects
also include PLATO \citep{Rauer14}, Earth 2.0
\citep{2022arXiv220606693G}, and the Roman Galactic Bulge Time Domain
Survey.  The surveys with good coverage of different regions of the
Galaxy seem most likely to yield new insight into whether the star
formation history we see in the Kepler field is universal across the
thin disk.

@@

We are grateful to Kento Masuda for thought-provoking discussions 
which significantly influenced our thinking about this analysis.
The work itself was supported by the Heising-Simons 51~Pegasi~b Fellowship
(LGB, EKP)
and the Arthur R.~Adams SURF Fellowship (EKP).

{\it \large Contributions}: Per \url{https://credit.niso.org/}:
Conceptualization: LGB.
Data curation: LGB, AWH, HI.
Formal analysis: LGB.
Funding acquisition: LGB.
Investigation: LGB, EKP.
Methodology: LGB, EKP.
Project administration: LGB, LAH, AWH.
Resources: LGB, AWH.
Software: LGB.
Supervision: LGB, LAH.
Validation: LGB.
Visualization: LGB.
Writing – original draft: LGB.
Writing – review \& editing: all authors.

>>>>

\author[0000-0002-0514-5538]{Luke~G.~Bouma}
\altaffiliation{51 Pegasi b Fellow}
\affiliation{\caltech}

@@

@@

\author[0000-0003-1298-9699]{Kento Masuda}
\affiliation{\osaka}

@@

{\it Field star ages from other surveys}:
While this study focused on Kepler, other photometric surveys
(e.g.~K2, TESS, HAT, WASP, NGTS, ZTF, ATLAS) open opportunities for
age-dating a far broader set of stars and planets.  Future prospects
also include PLATO \citep{Rauer14}, Earth 2.0
\citep{2022arXiv220606693G}, and the Roman Galactic Bulge Time Domain
Survey \citep{Wilson2023}.  Rotation-based age-dating from these surveys could
yield new insight
into whether the star formation history that we see in the Kepler field is
universal across the thin disk.

@@

The work itself was supported by the Heising-Simons 51~Pegasi~b Fellowship
(LGB, EKP) and the Arthur R.~Adams SURF Fellowship (EKP).
The HIRES spectra were obtained at the W.~M.~Keck Observatory.
We recognize the importance that the summit of Maunakea has always had
within the indigenous Hawaiian community, and we are deeply grateful 
for the opportunity to conduct observations from this mountain.

{\it \large Contributions}: Per \url{https://credit.niso.org/}:
Conceptualization: LGB.
Data curation: LGB, AWH, HI.
Formal analysis: LGB, KM.
Funding acquisition: LGB.
Investigation: LGB, EKP.
Methodology: LGB, EKP, KM.
Project administration: LGB, LAH, AWH.
Resources: LGB, AWH.
Software: LGB.
Supervision: LGB, LAH.
Validation: LGB, KM.
Visualization: LGB.
Writing – original draft: LGB.
Writing – review \& editing: all authors.
